\section*{Publications}

\textbf{Journal Articles}

\begin{enumerate}[leftmargin=*,noitemsep,nolistsep]

\item \textbf{Offline Navigation (Homing) of Aerial Vehicles (Quadcopters) in GPS-Denied Environments}.  
M. Mondal, S. Poslavskiy. \textit{Unmanned Systems}, vol. 9, no. 2, pp. 119--127, 2021.

\item \textbf{Designing LBP-Descriptor for Reconfigurable Computing Environments}.  
D.V. Shashev, A.A. Taganov, M. Mondal, M.V. Okunsky. \textit{Journal of Physics: Conference Series}, vol. 1611, no. 1, p. 012070, 2020.

\end{enumerate}

\vspace{0.05cm}
\textbf{Conference Proceedings}

\begin{enumerate}[leftmargin=*,noitemsep,nolistsep]

\item \textbf{Camera Assisted Autonomous UAV Landing}.  
M. Mondal, S. Shidlovskiy, D. Shashev. \textit{DCCN Workshop Proceedings}, 2020.

\item \textbf{Non-GNSS Navigation Systems in Aerial Vehicles (Multi-Rotors)}.  
M. Mondal, S. Shidlovskiy, D. Shashev, M. Khaddour. \textit{2021 International Conference on Information Technology (ICIT)}, pp. 451--455, 2021.

\item \textbf{Survey of Denoising Methods for Inertial Sensor Measurements}.  
M. Khaddour, S. Shidlovskiy, D. Shashev, M. Mondal. \textit{International Conference on Information Technology (ICIT)}, pp. 787--790, 2021.

\item \textbf{Aadhaar (India): A National Biometric Identification Program (Experience and Implementation)}.  
M. Mondal, S.L. Minkov. \textit{Innovatika}, 2019.

\item \textbf{Reconfigurable Flight-Controller Design in Simulink for Test-Implementing Interoperability of Components and Prototyping}.  
M. Mondal, M.V. Okunskiy. \textit{Intelligent Systems of the 4th Industrial Revolution}, pp. 98--99, 2022.

\item \textbf{Autonomous Infrared-Guided UAV Precision Landing System}.  
M. Mondal, S.V. Shidlovsky, D.V. Shashev, M.V. Okunsky. \textit{Distributed Computer and Communication Networks: 24th International Conference}, 2021.

\item \textbf{Implementation of an Open Source Communication Protocol (MAVLink) Between a Flight Controller and an On-Board Computer}.  
M. Mondal. \textit{Innovatika}, 2021.

\item \textbf{UAV Platform for Testing Autonomous Navigation Algorithms}.  
M. Mondal, S.V. Shidlovskiy. \textit{Innovatika}, 2020.

\item \textbf{Digital India: E-Government Initiative}.  
M. Mondal, S.L. Minkov. \textit{Innovatika}, 2020.

\item \textbf{Google Cartographer for Navigation and Mapping (SLAM)}.  
M. Mondal, S.I. Poslavskiy. \textit{Innovatika}, 2020.

\item \textbf{Cellular Network Control in Unmanned Aerial Vehicles}.  
M. Mondal, S.V. Shidlovskiy. \textit{Innovatika}, 2020.

\item \textbf{Aadhaar (India): National Biometric Identification Program (Experience and Implementation)}.  
M. Mondal, S.L. Minkov. \textit{Innovatika-2019: Proceedings of the XV International School-Conference}.

\item \textbf{Integration of SLAM and Obstacle Avoidance Algorithms}.  
S.I. Poslavskiy, M. Mondal. \textit{Innovatika-2019: Proceedings of the XV International School-Conference}.

\end{enumerate}