\section*{Work Experience}
\vspace{-0.05in}
\textbf{University of Connecticut (Cyber-Physical Systems Laboratory), Connecticut, USA.} \\
\textit{Research Assistant} \hfill 2022 – Present
\begin{itemize}[noitemsep,nolistsep]
    \item Designed and deployed MIND-CAVs, a browser-based CARLA orchestration system with LLM-assisted intent generation, FastAPI backend, React dashboard, and WebRTC streaming; supports real-time telemetry, scenario control, and dataset capture for closed-loop autonomy experiments.
    \item Developed autonomous driving features on F1Tenth and QCar robotic platforms using ROS on Nvidia Jetson TX2 SBC, implementing Lane Keeping, Obstacle Avoidance, SLAM, and Autonomous Waypoint Following; integrated and deployed open-source 5G stacks (OpenAirInterface and SRSRAN) to enable real-time V2V and V2I communication.
    % \item Developed autonomous driving features on an F1Tenth robotic platform using ROS on an Nvidia Jetson TX2, which implements Lane Keeping and Management, Obstacle Avoidance, SLAM, and an Autonomous Waypoint Follower.
    % \item Researched, ported and deployed open-source 5G stacks—OpenAirInterface 5G and SRSRAN—on prototype robotic systems (Quanser QCar and F1Tenth) and ARM-based Single Board Computers (SBCs) to enable millisecond-level and real-time communication for Vehicle-to-Infrastructure (V2I) and Vehicle-to-Vehicle (V2V) systems.
    \item Developed a Reinforcement Learning-based Charge-Scheduling Agent for Mobile Chargers in Wireless Powered Communication Networks, achieving a approximate 20\% higher average sensor survival rate while reducing travel distance by 5\%.
    \item Implemented autonomous driving features on a TurtleBot 3 platform using ROS, implemented Obstacle Avoidance, SLAM, and an Autonomous Waypoint Follower. Additionally, created an end-to-end control agent deployment pipeline using ROS.
\end{itemize}

\textbf{NR Tomsk State University (High Performance Reconfigurable Systems Laboratory), Tomsk, Russia.} \\
\textit{R\&D Engineer} \hfill 2018 – 2022
\begin{itemize}[noitemsep,nolistsep]
    \item Designed protocols and developed software for intercontinental Unmanned Aerial Vehicle (UAV) control and management, using ROS, Mavlink, Lightbridge and ZeroTier implementing a zero-trust network architecture to enable secure and reliable long-range remote operation.
    \item Designed an autonomous infrared-guided multirotor UAV landing system for safe landings in GPS-denied environments, improving landing precision by approximately 40\% on mobile landing zones.
    \item Designed a control algorithm for UAVs using Haversine’s Great Circle formula and PX4Flow, enabling autonomous Return-to-Home functionality in fail-safe conditions within GPS-denied environments.
    \item Developed prototype software and assembled multiple drones for automated medical and emergency supply delivery to quarantined areas during the COVID-19 pandemic, ensuring safe and efficient contactless distribution.
    \item Designed an Autonomous Scout/Attack UAV equipped with obstacle avoidance and autonomous flight routines. Integrated a low-altitude radar-based threat detection system that activates the UAV and initiates a scan upon object detection. Implemented an AlexNet-based CNN for real-time identification \& interception of aerial threats, neutralization using a net-gun capture mechanism.
    \item Engineered a Scout Tank designed for search and rescue operations, capable of navigating rough terrain and radiation-affected areas (Built to transport two humans and carry up to two 50kg payloads, with deployability in hazardous environments).
\end{itemize}

\textbf{Spar Up Sports Technologies Limited, Pune, India.} \\
\textit{Developer} \hfill 2017 – 2018
\begin{itemize}[noitemsep,nolistsep]
    \item Developed APIs for web platform features using the MEAN Stack and optimized the Hybrid Ionic App, reducing load times by 300\% for improved performance and user experience.
    \item Collaborated with clients to gather requirements, designed mockups, and developed personalized end-to-end features to enhance user experience and meet business needs.
\end{itemize}

\textbf{Tata Technologies Limited, Jamshedpur, India.} \\
\textit{Intern: Developer} \hfill 2016 (Nov – Dec)
\begin{itemize}[noitemsep,nolistsep]
    \item Researched and analyzed the existing paper and desktop-based Plant Complaint Management System to design and transition it into a scalable web-based application, improving accessibility, efficiency, and integration with modern enterprise systems.
    \item Developed the Plant Complaint Management System with a C\# backend and ASP.NET frontend, following SOLID principles for maintainability and scalability. Integrated the system with existing Inventory Management and General Management software to streamline operations and improve efficiency.
\end{itemize}