
\section*{Teaching Experience}

\textbf{University of Connecticut} \\
\textit{Teaching Assistant} \hfill 2023 – Present
\begin{itemize}[noitemsep,nolistsep]
    \item Conducted the Pre-College Robotics workshop (2024,2025) for 16 students, guiding them in designing and programming an autonomous 4-wheeled robot with computer vision.
    \item Prepared course materials and delivered the “C++ Essentials” course to over 200 students, focusing on industrial design patterns and SOLID principles to enhance software engineering best practices (Spring\textquotesingle23, 
 Fall\textquotesingle23, Spring\textquotesingle24, Fall\textquotesingle24, Spring\textquotesingle25).
\end{itemize}

\textbf{National Research Tomsk State University} \\
\textit{Teaching Assistant} \hfill 2019 – 2021
\begin{itemize}[noitemsep,nolistsep]
    \item Conducted a workshop on Applied AI in Unmanned Aerial Vehicles at Архипелаг 20.35 National Expo (2020), focusing on designing Multi-Rotor UAVs with Pixhawk Flight Controller and programming them using ROS, MAVLINK, and the Ardupilot stack. Also covered Simulation-in-the-Loop (SITL) using ROS, Gazebo, and Ardupilot SITL.
    \item Delivered a master class on DJI Onboard SDK at Архипелаг 20.35 National Expo (2020), focusing on autonomous navigation, terrain traversal, and long-range video transmission using the Lightbridge protocol.
    \item Prepared and delivered the “Embedded Systems” course, focusing on architecture design, intra-chip communication protocols, and single-board computing (Fall\textquotesingle19, Spring\textquotesingle20, Fall\textquotesingle20, Spring\textquotesingle21).
\end{itemize}

\textbf{Ed For All (Non-Profit Organization)} \\
\textit{Teacher/Coordinator} \hfill 2016 – 2017
\begin{itemize}[noitemsep,nolistsep]
    \item Taught basic English and math to over 100 underprivileged children in public schools across South India, fostering foundational literacy.
    \item Coordinated volunteers and the teaching team for weekly outreach camps in underprivileged and remote areas, organizing efforts to provide essential resources and education to under-served communities.
\end{itemize}